A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-28 10_applications.tex
sec. 5 and 6. a lot of comments, good luck

\subsection{Applications}
Because under- and overfill regions affect narrow parts more than wide parts, the use cases for this algorithm are centered around objects which contain thin parts.
Although the algorithm improves performance for all parts compared to existing techniques, the enhancement is percentually larger for thin parts.

\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading scheme.
Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
Also in larger regions and organic shapes (\cref{applications_case} and \subref{applications_statue}) our method finds succesful application.

Architectural models and casings benefit from preventing very thin regions from being filled at all and from the prevention of over- and underfill within thin walls, which makes them stronger.
Embossed text benefits from the prevention of underfill areas, which would cause various holes in top surfaces, which is detrimental to the visual quality of those top surfaces.
Gears benefit from the preventio of under- and overfill regions and the distributed bead width discrepancy in that the mechanical properties of the toolpath are more consistent throughout.

Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties more closely matching homogenized mechanical properties.
For example the result of a topology optimized structure can contain filaments of varying thickness \cite{wu2017infill} which follow a varying stress distribution (\cref{applications_bone}).
Also microstructures with homogenous thickness in the direction perpendicular to the surface of the microstructure can result in horizontal cross-sections with varying thickness;
\cref{applications_gyroid} shows how an angled gyroid structure with homogenous thickness results in heterogeneous outline shapes.
Another class of microstructures consists of homogenous patterns which employ varying thickness in order to achieve a functionally graded material.
\Cref{applications_hex} shows how the toolpathing of a hexagonal grid neatly switches between different bead counts over the volume, which prevents the jagged moves a direction parallel infill pattern would create for such a case. \cite{bates2018compressive}

>>>>

\subsection{Applications}
Toolpath with varying width is particularly meaningful for narrow parts, since there the negative effect of under- and overfill is more pronounced than in wide parts.
In extreme cases, thin features might not be filled at all.
Therefore, our framework, while working for wide parts as well, shows most of its potential for objects which contain thin parts.

\Cref{applications_overview} collectively shows the application of the proposed inward distributed scheme for various types of 3D model, including both thin parts (architectural models, casings, embossed text, gears and microstructures) and wide parts (larger regions (\cref{applications_case}) and organic shapes (\cref{applications_statue})).

For architectural models and casings, the prevention of over- and underfill is expected to make them stronger. 
For embossed text, the prevention of underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
Gears benefit from the prevention of under- and overfill regions and the distributed bead width discrepancy in that the mechanical properties of the toolpath are more consistent throughout. \jun{I don't follow the benefit for gears}

Of particular interest are microstructures that could be uniquely fabricated by 3D printing.
Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties closer to expectation.
For example, topology optimized bone-like structures~\cite{wu2017infill} contain filaments of varying thickness that follow a varying stress direction (\cref{applications_bone}).
An angled Gyroid structure with uniform thickness results in outline shapes with varying width (\cref{applications_gyroid}).
Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.
\Cref{applications_hex} shows the contour-parallel toolpath with varying width of a hexagonal grid neatly switches between different bead counts over the volume, preventing the jagged moves a direction-parallel toolpath would create for such a case~\cite{bates2018compressive}.

### 2019-08-28 6_validation.tex
sec. 5 and 6. a lot of comments, good luck

\section{Validation}
We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$. The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

\subsection{Computational analysis}

The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The number of elements in the ST is linear in the number of elements in the VD
and all of the stages of our framework are also linear in the number of elements in the ST,
so the total running time of our algorithm is $O(n \log n)$.

From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2 \times 10^{-5} n \log n$ seconds.
The computation time is approximately five times the computation time of the uniform technique, which puts it in the same order of magnitude.

\subsubsection{Accuracy}
In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the extrusion segment, we would get artifacts at corners in the toolpath (\cref{segment_visualization}a).
We therefore use a semi-circle (\cref{segment_visualization}b) with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position ( \cref{segment_visualization}c).

@@

We calculated the total overfill and underfill areas of the different toolpath schemes applied on the data set. 
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.

@@

\paragraph{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive extrusion segments generated by each scheme.
The relative frequency of these angles is shown in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
The inward distributed scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}.

\subsection{Experimentation}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.

>>>>

\section{Validation}
\jun{section title -> Results?}

We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$. The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

\subsection{Computational results}

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the amount of the overfill and underfill. 
This is compared on a slice of a \jun{?} model, as shown in \cref{visualized_accuracy} (top).
\jun{discuss this figure a bit}

We further quantitatively compare the accuracy of the beading schemes on the data set. 
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.

In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the extrusion segment, we would get artifacts at corners in the toolpath (\cref{segment_visualization}a).
We therefore use a semi-circle (\cref{segment_visualization}b) with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position ( \cref{segment_visualization}c).

@@

@@

\subsubsection{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We measured the angle between consecutive extrusion segments generated by each scheme.
The relative frequency of these angles is shown in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
The inward distributed scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}.

\subsubsection{Computational performance}
\cref{computime} plots the computation time for each of the 300 slices against the vertex count of the layer, comparing the uniform technique~\cite{johnson2014clipper} and our framework with the inward distributed scheme. For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.

The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The other steps in our framework have a complexity of $O(n)$ or $O(m)$, where $m$ is the number of elements in the ST.
Therefore, the total running time of our algorithm is $O(n \log n)$. Results in \cref{computime} conform that both our framework and the uniform technique have an expected running time of approximately $5 \times 10^{-6} n \log n$ seconds.
% The computation time of our framework is approximately five times that of the uniform technique, which puts it in the same order of magnitude.

\subsection{Printing results}
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control~\cite{tronvoll2019investigating}. \jun{sentence too long}
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines thinner than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
\jun{discuss the positive aspects of the new beading by 2~3 sentences}

### 2019-08-28 8_discussion.tex
sec. 5 and 6. a lot of comments, good luck

\subsection{Comparison of beading schemes}
The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.

We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
These defects surely influence the mechanical properties of the parts beyond a point that process parameters can reliably be correlated to mechanical properties of the part.

@@

For an input outline shape which contains both very small and very large features, the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.

If we look at \cref{TEST_Center_accuracy} we can see that
the centered beading scheme effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.

However, according to \cref{widthHistogram} the centered scheme exhibits a lot wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the distributed schemes is approximately \SI{14}{\micro\meter}.
We can therefore state that the distributed schemes result in bead widths closer to the nominal widths compared to the centered scheme.
This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

The inward distributed beading scheme was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.

However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all. 
Also, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}). 
Therefore, when using the Inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.

\subsection{Theoretical analysis}
In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
The significance measure is an exact measure of the relative size of gaps when using the uniform toolpathing method.
See \cref{naive_overfill_underfill}
Note also that contrary to some literature we do not remove edges from the skeleton, but leave it intact.
The final skeleton is still an exact and full feature descriptor.
In that sense our framework provides an exact solution space.

Note also that our method is robust against small perturbations in the input shape.
Geometrically small changes to the outline shape introduce extra edges and therefore change the topology of the graph of the ST.
However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there was no such edge in that region.
The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.

Our framework is also local.
The toolpathing around some section of the input polygons is independent of far away regions of the polygon.
This means the toolpathing is stable against large perturbations of the input shape in far away regions
and it also allows for some parallelism during the computation of the toolpaths.

\subsection{Limitations}
In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w^*$.
That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
which might be difficult to accurately manufacture on some hardware.
While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around sites in the toolpath, so this approach is inherently limited.
Our schemes require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms~\cite{tronvoll2019investigating}.
Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.

Another limiting factor in the adoption of adaptive bead width is that Gcode -- a common file format for storing machine instructions -- does not support  moves with varying cross-sectional area.
A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed across the extrusion move.
This could be mediated by discretizing a variable width extrusion segment into smaller segments, but that approach might still result in some small inaccuracies.
Ideally the Gcode language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.

Taking a broader perspective, we note that our proposed inward distributed scheme is a pragmatic solution.
Rather than deriving some optimal beading scheme from a clear specification of the objective, we propose some arbitrary inward distributed beading scheme and show that it is better than the other beading schemes.
An optimal beading scheme can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading scheme.

>>>>

\subsection{Comparison of beading schemes}
%The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.

We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
These defects are supposed to negatively influence the mechanical properties of the parts, and exceed the point that process parameters can be reliably correlated to mechanical properties of the part. 
To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.

@@

For an input outline shape which contains both very small and very large features, the algorithm \jun{which specific scheme, or our method in general?} produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.

In \cref{TEST_Center_accuracy} we can see that
the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except in the center the bead widths are within a factor 2 off from the desired bead width.
According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.

However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
We can therefore state that the distributed schemes result in bead widths closer to the nominal widths compared to the centered scheme.
This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

The inward distributed scheme is introduced with the intention to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
This expected effect is difficult to be confirmed when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.

However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all. 
Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}). 
Therefore, when using the inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.

\subsection{Theoretical analysis}
\jun{I suggest to dissolve this subsection. see comments and suggested changes below.}

In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
The significance measure is an exact measure of the relative size of gaps when using the uniform toolpathing method.
See \cref{naive_overfill_underfill}
\jun{this is in the method, and thus can be removed.}
Note also that contrary to some literature we do not remove edges from the skeleton, but leave it intact.
The final skeleton is still an exact and full feature descriptor.
In that sense our framework provides an exact solution space.
\jun{what is a solution space? what is the benefit of using an exact and full feature descriptor regarding toolpath accuracy, uniformity and smoothness?}

Note also that our method is robust against small perturbations in the input shape.
Geometrically small changes to the outline shape introduce extra edges and therefore change the topology of the graph of the ST.
However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton. \jun{this could be mentioned somewhere in the method, shortly. The uniform approach can also be thought of using the distance field, is it less robust than ours?}
Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there was no such edge in that region.
The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.
\jun{this could be integrated in paragraph Smooth transitions to motivate the fractional bead count}

Our framework is also local.
The toolpathing around some section of the input polygons is independent of far away regions of the polygon.
This means the toolpathing is stable against large perturbations of the input shape in far away regions
and it also allows for some parallelism during the computation of the toolpaths.
\jun{This could mentioned in paragraph Computational performance. This potentially could be parallelized for speeding up.}

\subsection{Limitations}
\jun{postpone this subsection to Applications}
We note that printing with varying width is not the current standard in FDM printing.
It calls for adaptations and developments in printers and the workflow.
In the beading schemes we set a transition length of $t(n) = w^*$.
That might demand \jun{can we say, "while it rarely happens, it may demand ..."} changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size.
This is challenging for some hardware.
The effect of varying the movement speed to change the cross-sectional area is limited, since the movement speed is constrained by acceleration considerations around sites in the toolpath.
Our schemes require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement \jun{in terms of what? can we say, "... shall improve ... significantly"} over Bowden style FDM printers,
but still requires some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
We expect the development in printing hardware will address these challenges in the future.

Another limiting factor in the adoption of adaptive bead width is G-code which stores machine instructions. G-code does not support moves with varying cross-sectional area.
A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed across \jun{along?} the extrusion move.
A workaround is to approximate a variable width extrusion segment by smaller segments with constant width. This, nevertheless, introduces errors.
Ideally the G-code language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.

% Taking a broader perspective, we note that our proposed inward distributed scheme is a pragmatic solution.
% Rather than deriving some optimal beading scheme from a clear specification of the objective, we propose some arbitrary inward distributed beading scheme and show that it is better than the other beading schemes.
% An optimal beading scheme can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
% This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading scheme.
